---
title: "Angola Onchocerciasis Elimination Mapping"
output:
  html_document: 
  keep_md: yes
word_document: default
pdf_document: default
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	fig.asp = 0.8,
	fig.height = 12,
	fig.retina = 2,
	fig.width = 12,
	include=FALSE,
	warning = FALSE,
	cache = TRUE,
	dev = "png",
	dpi = 300,
	include = FALSE,
	out.width = "100%"
)
require(pacman)
pacman::p_load(raster, sf, exactextractr, here, 
               leaflet, leaflet.extras, 
               janitor, patchwork,RColorBrewer,
               ggsn,gghighlight,ggsflabel,ggbeeswarm)
library(tidyverse)


# conflict_prefer("select", "dplyr")
# conflict_prefer("filter", "dplyr")
# conflict_prefer("scalebar", "ggsn")
# conflict_prefer("geom_sf_label", "ggsflabel")

myPalette <- colorRampPalette(rev(brewer.pal(11, "Spectral")))
sc <- scale_fill_gradientn(colours = myPalette(100), limits=c(0, 1))

```

Selecting municipalities for Onchocerciasis elimination mapping (OEM) can be supported by evidence from publicly available data on endemicity status and environmental suitability.

## Data sources

The data for mapping the Implementation Units (IUs) are from the [ESPEN data portal](https://espen.afro.who.int/sites/default/files/content/cartography/files/ESPEN_IU_2020_0.zip). There are 164 implementation units in Angola.

```{r angola-map}
ang_shp <-
  read_sf(here('data', 'input', 'shp', 'ESPEN_IU_2020.shp')) %>%
  dplyr::filter(ADMIN0 == 'Angola')

# map_options <- north(ang_shp) +
#   scalebar(ang_shp, dist = 250, dist_unit = "km",
#            transform = TRUE, model = "WGS84")

adm3_shp <-
  read_sf(here(
    'data',
    'input',
    'shp',
    'ago_admbnda_adm3_gadm_ine_ocha_20180904.shp'
  ))

adm1_shp <- adm3_shp %>%
  group_by(ADM1_EN) %>%
  summarise()

adm2_shp <- adm3_shp %>%
  group_by(ADM2_EN) %>%
  summarise()

ang_map <- ggplot() +
  geom_sf(
    fill = "transparent",
    color = "blue",
    size = 1,
    data = ang_shp
  ) +
  geom_sf(
    fill = "transparent",
    color = "red",
    size = 1.5,
    data = adm1_shp
  ) 
  # north(ang_shp) +
  # scalebar(
  #   ang_shp,
  #   dist = 250,
  #   dist_unit = "km",
  #   transform = TRUE,
  #   model = "WGS84"
  # )

ang_map
rm(ang_map)
```

The data for the environmental suitability were produced by the IHME and are available [here](http://ghdx.healthdata.org/record/ihme-data/africa-onchocerciasis-environmental-suitability-geospatial-estimates). The data are presented as 5x5 km squares and a full description of the methods can be found [here](https://journals.plos.org/plosntds/article?id=10.1371/journal.pntd.0008824). Variables in the analysis include climate, vegetation, vector breeding sites and whether an area is rural or urban. The suitability score is from 0 (low suitability) to 100 (high suitability).

```{r angola-map-raster}

# Import raster data in raster format
africa_oncho_raster <- raster::raster(here('data', 'IHME_AFRICA_ONCHO_ENV_SUIT_MEAN_Y2020M08D26.TIF'))

angola_oncho_raster_crop <- crop(africa_oncho_raster, ang_shp)

angola_oncho_point  <-  rasterToPoints(angola_oncho_raster_crop)
angola_oncho_point_df <-  data.frame(angola_oncho_point)
colnames(angola_oncho_point_df) = c("lon", "lat", "suitability")

ang_raster_map <- ggplot(ang_shp) +
  geom_sf() +
  geom_raster(data = angola_oncho_point_df, aes(lon, lat, fill = suitability/100), alpha = .7) +
  geom_sf(fill = "transparent", color = "black", size = 1.5, 
          data = adm1_shp) +
  labs(fill='Environmental suitability', x='', y='') +
  theme(legend.position='top') +
  sc +
  ggsn::north(ang_shp) +
  ggsn::scalebar(ang_shp, dist = 250, dist_unit = "km",
           transform = TRUE, model = "WGS84")

ang_raster_map

rm(ang_raster_map,angola_oncho_raster_crop)
```

Data on endemicity are available from the [ESPEN data portal](https://espen.afro.who.int/countries/angola).

```{r angola-map-endemicity}
ang_espen_data <-
  read.csv(here('data', 'input', 'espen_platform_oncho.csv')) %>%
  filter(Year == 2020)

unknown_iu <-
  ang_espen_data %>% 
  filter(grepl('Unknown', Endemicity)) %>% 
  pull(IU_ID)

ang_endemicity_map <- ang_shp %>%
  left_join(ang_espen_data,
            by = c('ADMIN1ID', 'ADMIN2ID', 'ADMIN3ID', 'IU_ID')) %>%
  ggplot() +
  geom_sf(aes(fill = Endemicity)) +
  geom_sf(
    fill = "transparent",
    color = "black",
    size = 1.5,
    data = adm1_shp
  ) +
  labs(fill = 'Onchocerciasis endemicity categories (2020)') +
  theme(legend.position = c(0.85, 0.9)) +
  north(ang_shp) +
  scalebar(
    ang_shp,
    dist = 250,
    dist_unit = "km",
    transform = TRUE,
    model = "WGS84"
  )

ang_endemicity_map

ang_endemicity_tbl <- ang_espen_data %>%
  tabyl(Endemicity) %>%
  adorn_pct_formatting(rounding = "half up", digits = 0) %>%
  knitr::kable()
ang_endemicity_tbl

rm(ang_endemicity_map, ang_endemicity_tbl)


```

As of 2020, there were 116 IUs with unknown endemicity. MDA for lymphatic filariasis (LF) was reported in 28 of these 116 IUs.

```{r lf-mapping}
lf_raw <- read.csv(here('data', 'input', 'espen_platform_lf.csv'))

lf_wd <- lf_raw %>%
  rename(lf_status = Endemicity,
         lf_mda = MDA_scheme)

ang_lf_endemicity_data <- ang_shp %>%
  left_join(lf_wd %>%
              filter(Year == 2020), by = 'IU_ID') %>%
  filter(IU_ID %in% unknown_iu)

lf_endemicity_map <- ggplot() +
  geom_sf(data = ang_lf_endemicity_data,
          aes(fill = lf_status),
          color = "gray50",
          size = 0.5) +
  geom_sf(
    fill = "transparent",
    color = "black",
    size = 1.5,
    data = adm1_shp
  ) +
  scale_fill_discrete(na.translate = F) +
  labs(fill = '') +
  theme(legend.position = c(0.85, 0.9))

lf_endemicity_map
```



```{r oncho-loaloa-lf-mapping}
oncho_raw <-
  read.csv(here('data', 'input', 'espen_platform_oncho.csv'))

oncho_wd <- oncho_raw %>%  rename(oncho_status = Endemicity,
                                  oncho_mda = MDA_scheme)

oncho_unknown_ius <-
  oncho_wd %>% filter(grepl("Unknown", oncho_status)) %>% pull(IU_ID)

loa_loa_raw <-
  read.csv(here('data', 'input', 'espen_platform_loaloa.csv'))

loa_loa_wd <- loa_loa_raw %>%
  rename(loaloa_status = Endemicity)

all_diseases <- oncho_wd %>%
  left_join(loa_loa_wd, by = c('ADMIN1', 'IU_ID', 'Year')) %>%
  left_join(lf_wd, by = c('ADMIN1', 'IU_ID', 'Year'))

all_diseases_summary <- all_diseases %>%
  mutate(
    oncho_endemic = case_when(grepl("Endemic", oncho_status) ~ "Yes",
                              TRUE ~ "Unknown"),
    loaloa_endemic = case_when(grepl("Endemic", loaloa_status) ~ "Yes",
                               TRUE ~ "No"),
    lf_endemic = case_when(
      grepl("\\<Endemic\\>", lf_status) ~ "Yes",
      grepl("\\<Non-endemic\\>", lf_status) ~ "No",
      TRUE ~ "Unknown"
    )
  )

ang_shp <-
  read_sf(here('data', 'input', 'shp', 'ESPEN_IU_2020.shp')) %>%
  filter(ADMIN0 == 'Angola')

ang_adm3_shp <-
  read_sf(here(
    'data',
    'input',
    'shp',
    'ago_admbnda_adm3_gadm_ine_ocha_20180904.shp'
  ))

endemicity_categories <- all_diseases_summary %>%
  filter(Year == 2020, oncho_endemic == "Unknown") %>%
  filter(IU_ID %in% oncho_unknown_ius) %>%
  select(IU_ID, oncho_endemic, loaloa_endemic, lf_endemic) %>%
  mutate(final_endemicity = paste(loaloa_endemic, lf_endemic, sep = "-"))

ang_endemicity_data <- ang_shp %>%
  left_join(endemicity_categories,
            by = c('IU_ID'))

oncho_loaloa_lf_combined_map1 <- ggplot() +
  geom_sf(
    data = ang_endemicity_data,
    aes(fill = final_endemicity),
    color = "gray50",
    size = 0.5
  ) +
  geom_sf(
    fill = "transparent",
    color = "black",
    size = 1.5,
    data = adm1_shp
  ) +
  labs(fill = 'Loaloa-LF') +
  scale_fill_discrete(na.translate = F) +
  theme(legend.position = 'top')

oncho_loaloa_lf_combined_map1

oncho_loaloa_lf_combined_map2 <- ggplot() +
  geom_sf(
    data = ang_endemicity_data %>% filter(!is.na(final_endemicity)),
    aes(fill = final_endemicity),
    color = "gray50",
    size = 0.5
  ) +
  geom_sf(
    fill = "transparent",
    color = "black",
    size = 1.5,
    data = adm1_shp
  ) +
  scale_fill_discrete(na.translate = F) +
  labs(fill = 'Loaloa-LF') +
  theme(legend.position = 'top') +
  facet_wrap( ~ final_endemicity)

oncho_loaloa_lf_combined_map2
```


To prioritise IUs for mapping, we can focus on the 116 IUs classified as "Unknown". We can also use the environmental suitability to reduce the number of IUs for consideration.

```{r angola-map-unknown-endemicity}
# Load oncho environmental suitability raster data
africa_oncho_rs <-
  stack(here('data', 'IHME_AFRICA_ONCHO_ENV_SUIT_MEAN_Y2020M08D26.TIF'))

#Crop raster to Angola shapefile
angola_oncho_combined <-
  exact_extract(africa_oncho_rs,
                ang_shp,
                progress = FALSE)  %>%
  bind_rows(., .id = "id") %>%
  as_tibble()

#--- weighted mean ---#

oncho_by_id <- angola_oncho_combined %>%
  #--- convert from character to numeric  ---#
  mutate(id = as.numeric(id)) %>%
  #--- group summary ---#
  group_by(id) %>%
  filter(!is.na(value)) %>%
  summarise(oncho_mean_aw = sum(value * coverage_fraction) / sum(coverage_fraction))

#--- merge ---#
oncho_angola <- ang_shp %>%
  mutate(id := seq_len(nrow(.))) %>%
  left_join(., oncho_by_id, by = "id") %>%
  dplyr::select(id, oncho_mean_aw, 'ADMIN1ID', 'ADMIN2ID', 'ADMIN3ID', 'IU_ID') %>%
  left_join(ang_espen_data,
            by = c('ADMIN1ID', 'ADMIN2ID', 'ADMIN3ID', 'IU_ID'))

oncho_angola_mean_env_iu <- oncho_angola %>%
  as.data.frame() %>%
  select('ADMIN1ID', 'ADMIN2ID', 'ADMIN3ID', 'IU_ID', 'oncho_mean_aw')

# Quick map to check data
ang_unknown_endemicity_map <- oncho_angola %>%
  mutate(oncho_mean_aw = ifelse(grepl('Unknown', Endemicity), oncho_mean_aw,
                                NA)) %>%
  ggplot() +
  geom_sf(aes(fill = oncho_mean_aw)) +
  geom_sf(
    fill = "transparent",
    color = "black",
    size = 1.5,
    data = adm1_shp
  ) +
  labs(fill = 'Environmental suitability') +
  theme(legend.position = 'top') +
  sc +
  north(ang_shp) +
  scalebar(
    ang_shp,
    dist = 250,
    dist_unit = "km",
    transform = TRUE,
    model = "WGS84"
  )

ang_unknown_endemicity_map

rm(africa_oncho_rs, ang_unknown_endemicity_map, oncho_by_id)
```

This map shows the weighted mean environmental suitability for IUs with unknown endemicity. Several IUs in Northern Angola have very high environmental suitability scores.

In the centre of the country, there are several IUs with moderate environmental suitability scores in the Huambo region.

A critical limitation of this analysis is that by calculating an aggregate score, in this case, a weighted mean, for each IU, there will be some IUs with a low aggregate score that contains several areas with high environmental suitability scores. This can be demonstrated by looking at Huambo province.

## Environmental suitability threshold

In the paper describing the methods and results of the predicted environmental suitability, a mean prediction of \>=71 to have the highest probability of environmental suitability.

We can use this value as an additional filter to identify implementation units in Angola with unknown endemicity and at least one 5 x 5-km location reaching this threshold.

```{r angole-env-byprovince}

africa_oncho_rs <- stack(here('data', 'IHME_AFRICA_ONCHO_ENV_SUIT_MEAN_Y2020M08D26.TIF'))

#Crop raster to Angola shapefile
angola_oncho_raster_df <- 
  exact_extract(
    africa_oncho_rs, 
    ang_shp,
    progress = FALSE
  )  %>% 
  bind_rows(., .id = "id") %>% 
  as_tibble() %>% 
  #--- convert from character to numeric  ---#
  mutate(id = as.numeric(id)) %>% 
  #--- group summary ---#
  group_by(id) %>% 
  filter(!is.na(value)) 

#--- merge ---#
oncho_angola_env_threshold <- ang_shp %>% 
  mutate(id := seq_len(nrow(.))) %>% 
  left_join(., angola_oncho_raster_df, by = "id") %>% 
  dplyr::select(id, 'ADMIN1ID', 'ADMIN2ID', 'ADMIN3ID', 'IU_ID', 'value') %>% 
  left_join(ang_espen_data, by=c('ADMIN1ID', 'ADMIN2ID', 'ADMIN3ID', 'IU_ID'))  %>% 
  filter(IU_ID %in% unknown_iu)

angola_beeswarm_gph <- oncho_angola_env_threshold %>% 
  #filter(IU_ID %in% unknown_iu) %>% 
ggplot(.,aes((ADMIN2), value)) + geom_quasirandom() +
  geom_hline(yintercept = 71,
             color = "red", size=1, linetype="dashed") +
  labs(y = "Environmental suitability (0=lowest, 100=highest)", x = "", title = "Onchocerciasis environmental suitability score for implementation units with unknown onchocerciasis endemicity", subtitle = "Red dashed line at threshold value (>=71) for environmental suitability. Above this point, areas have high susceptibility") +
  coord_flip() +
  theme(legend.position='top') +
  facet_wrap(~ ADMIN1, scales='free_y', ncol=6)

angola_beeswarm_gph

```

```{r angola-env-prop-over71}

prop_over71 <- oncho_angola_env_threshold %>% 
  as_tibble() %>% 
  filter(IU_ID %in% unknown_iu) %>% 
  mutate(over71=case_when(value>=71 ~1, 
                          TRUE ~0)) %>% 
  select(IU_ID, over71) %>% 
  count(IU_ID,over71) %>% 
  group_by(IU_ID) %>% 
  mutate(prop_over71=100*(n/sum(n))) %>% 
  filter(over71==1) %>% 
  select(IU_ID, prop_over71)

prop_over71_map <- ang_shp %>%
  left_join(prop_over71,
            by = c('IU_ID')) %>%
  ggplot() +
  geom_sf(aes(fill = prop_over71)) +
  scale_fill_continuous(type = "viridis") +
  geom_sf(fill = "transparent", color = "black", size = 1.5,
          data = adm1_shp) +
  labs(fill='% of IU >=71 environmental suitability score') + 
  theme(legend.position=c(0.85, 0.9)) +
  north(ang_shp) +
  scalebar(ang_shp, dist = 250, dist_unit = "km",
           transform = TRUE, model = "WGS84")
  
```


```{r angola-env-exceeds71}

exceeds71 <- angola_oncho_point_df %>% 
  filter(suitability>=71)

exceeds71_map <- ggplot(ang_shp) +
  geom_sf()+
  geom_raster(data = exceeds71, aes(lon, lat, fill = suitability), alpha = .7) +
    geom_sf(fill = "transparent", color = "black", size = 1.5, 
          data = adm1_shp) +
  labs(fill='Environmental suitability') +
  theme(legend.position='top') +
  sc +
  north(ang_shp) +
  scalebar(ang_shp, dist = 250, dist_unit = "km",
           transform = TRUE, model = "WGS84")

exceeds71_map

rm(angola_oncho_point_df,exceeds71_map)
```

```{r angola-unknownendemicity-exceeds71}
exceeds71_raster <- angola_oncho_combined %>% 
  filter(value>=71)

exceeds71_by_id <- exceeds71_raster %>% 
  #--- convert from character to numeric  ---#
  mutate(id = as.numeric(id)) %>% 
  #--- group summary ---#
  group_by(id) %>% 
  filter(!is.na(value)) %>% 
  count(id)
#summarise(oncho_mean=mean(value))
#summarise(oncho_mean_aw = sum(value * coverage_fraction) / sum(coverage_fraction))


#--- merge ---#
exceeds71_oncho <- ang_shp %>% 
  mutate(id := seq_len(nrow(.))) %>% 
  left_join(., exceeds71_by_id, by = "id") %>% 
  dplyr::select(id, n, 'ADMIN1ID', 'ADMIN2ID', 'ADMIN3ID', 'IU_ID') %>% 
  left_join(ang_espen_data, by=c('ADMIN1ID', 'ADMIN2ID', 'ADMIN3ID', 'IU_ID')) %>% 
  mutate(n = ifelse(grepl('Unknown', Endemicity),n,
                    NA))


# Quick map to check data
exceeds71_oncho_map <- exceeds71_oncho %>% 
  ggplot() +
  geom_sf(aes(fill=n)) +
    geom_sf(fill = "transparent", color = "black", size = 1.5, 
          data = adm1_shp) +
  labs(fill='Number of locations with high environmental suitability') +
  theme(legend.position='top') +
  scale_fill_viridis_c(option = "heat",begin = 0.1)
#sc +
#north(ang_shp) +
#scalebar(ang_shp, dist = 250, dist_unit = "km",
#  transform = TRUE, model = "WGS84")


exceeds71_oncho_map
rm(exceeds71_oncho_map,exceeds71_raster)
```

```{r}
iu_env_suitability <- exceeds71_oncho %>% 
  as.tibble() %>% 
  filter(n>0) %>% 
  select(IU_ID,Endemicity,n)

iu_env_suitability_list <- iu_env_suitability %>% pull(IU_ID)
```

There are `r nrow(iu_env_suitability)` implementation units with unknown endemicity and at least one pixel with an environmental suitability score \>=71.

Filtering the implementation units that have unknown endemicity.

```{r}
ang_unknown_endemicity_env_suitability_map <- oncho_angola %>% 
  mutate(oncho_mean_aw = ifelse(IU_ID %in% iu_env_suitability_list,oncho_mean_aw,NA)) %>% 
  mutate(oncho_mean_aw = ifelse(grepl('Unknown', Endemicity),oncho_mean_aw,NA)) %>% 
  ggplot() +
  geom_sf(aes(fill=oncho_mean_aw)) +
    geom_sf(fill = "transparent", color = "black", size = 1.5, 
          data = adm1_shp) +
  labs(fill='Environmental suitability') +
  theme(legend.position='top') +
  sc +
  north(ang_shp) +
  scalebar(ang_shp, dist = 250, dist_unit = "km",
           transform = TRUE, model = "WGS84")


ang_unknown_endemicity_env_suitability_map

```

```{r angola-loaloa-map}
ang_espen_loaloa_data <-
  read.csv(here('data', 'input', 'espen_platform_loaloa.csv')) %>%
  filter(Year == 2020) %>% 
  filter(IU_ID %in% oncho_unknown_ius)

ang_endemicity_loaloa_map <- ang_shp %>%
  left_join(ang_espen_loaloa_data,
            by = c('ADMIN1ID', 'ADMIN2ID', 'ADMIN3ID', 'IU_ID')) %>%
  ggplot() +
  geom_sf(aes(fill = Endemicity)) +
  geom_sf(fill = "transparent", color = "black", size = 1.5,
          data = adm1_shp) +
  labs(fill='') + 
    scale_fill_discrete(na.translate = F) +
  theme(legend.position=c(0.85, 0.9)) +
  north(ang_shp) +
  scalebar(ang_shp, dist = 250, dist_unit = "km",
           transform = TRUE, model = "WGS84")

ang_endemicity_loaloa_map

ang_endemicity_loa_loa_tbl <- ang_espen_loaloa_data %>%
  tabyl(Endemicity) %>%
  adorn_pct_formatting(rounding = "half up", digits = 0) %>%
  knitr::kable()

#rm(ang_endemicity_loaloa_map,ang_endemicity_loa_loa_tbl)
```

```{r angola-loaloa-endemicity-envsuitability-map}

iu_loaloa_list <- ang_espen_loaloa_data %>% 
  filter(Endemicity!='Endemic') %>% 
  pull(IU_ID)

ang_loaloa_unknown_endemicity_env_suitability_map <- oncho_angola %>% 
  mutate(oncho_mean_aw = ifelse(IU_ID %in% iu_env_suitability_list,oncho_mean_aw,NA)) %>% 
  mutate(oncho_mean_aw = ifelse(grepl('Unknown', Endemicity),oncho_mean_aw,NA)) %>% 
  mutate(oncho_mean_aw = ifelse(IU_ID %in% iu_loaloa_list,oncho_mean_aw,NA))  %>% 
  ggplot() +
  geom_sf(aes(fill=oncho_mean_aw)) +
    geom_sf(fill = "transparent", color = "black", size = 1.5, 
          data = adm1_shp) +
  scale_fill_discrete(na.translate = F) +
  labs(fill='Environmental suitability') +
  theme(legend.position='top') +
  sc +
  north(ang_shp) +
  scalebar(ang_shp, dist = 250, dist_unit = "km",
           transform = TRUE, model = "WGS84")


ang_loaloa_unknown_endemicity_env_suitability_map

env_suitability_unk_endemicity_no_loaloa <- oncho_angola %>% 
  filter(grepl('Unknown', Endemicity)) %>% 
  filter(IU_ID %in% iu_env_suitability_list) %>% 
  filter(IU_ID %in% iu_loaloa_list)


```

```{r huambo-map}

huambo_unknown <- ang_espen_data %>% 
  as.data.frame() %>% 
  filter(ADMIN1=='Huambo') %>% 
  filter(grepl('Unknown', Endemicity)) %>% 
  filter(IU_ID %in% iu_env_suitability_list) %>% 
  filter(IU_ID %in% iu_loaloa_list) %>% 
  pull(IU_ID)

huambo_oncho_map <- oncho_angola %>% 
  #filter(grepl('Unknown', Endemicity)) %>% 
  #filter(ADMIN1=='Huambo') %>% 
  ggplot() +
  geom_sf(aes(fill=ADMIN1), lwd=1) +
  gghighlight(IU_ID %in% huambo_unknown) +
    geom_sf(fill = "transparent", color = "black", size = 1.5, 
          data = adm1_shp) +
  geom_sf_label_repel(aes(label = IUs_NAME),
                      force = 100, nudge_x = -2, seed = 10) +
  labs(fill='') +
  theme(legend.position='top') +
  # geom_sf_label_repel(aes(label = IUs_NAME),
  #                      force = 100, nudge_x = -2, seed = 10) +
  #sc +
  north(ang_shp) +
  scalebar(ang_shp, dist = 250, dist_unit = "km",
           transform = TRUE, model = "WGS84")

huambo_oncho_map
rm(huambo_oncho_map)
```

```{r huambo-env-suitability2}

huambo_shp <- ang_shp %>% 
  filter(IU_ID %in% huambo_unknown) 

huambo_oncho_crop <- crop(africa_oncho_raster, huambo_shp)

huambo_oncho_point  <-  rasterToPoints(huambo_oncho_crop)
huambo_oncho_point_df <-  data.frame(huambo_oncho_point)
colnames(huambo_oncho_point_df) = c("lon", "lat", "oncho_mean_aw")

huambo_raster_map <- ggplot(huambo_shp) +
  geom_raster(data = huambo_oncho_point_df, aes(lon, lat, fill = oncho_mean_aw), alpha = .7) +
  theme(legend.position = "none") +
  geom_sf(fill=alpha(0.2)) +
  labs(fill='Environmental suitability') +
  theme(legend.position='top') +
  sc +
  north(huambo_shp) +
  scalebar(huambo_shp, dist = 50, dist_unit = "km",
           transform = TRUE, model = "WGS84")

#huambo_raster_map

huambo_unknown_endemicity_map <- oncho_angola %>% 
  filter(grepl('Unknown', Endemicity)) %>% 
  filter(ADMIN1=='Huambo') %>% 
  filter(IU_ID %in% huambo_unknown) %>% 
  #filter(IU_ID %in% iu_env_suitability_list) %>% 
  ggplot() +
  geom_sf(aes(fill=oncho_mean_aw), lwd=1) +
  labs(fill='Environmental suitability') +
  theme(legend.position='top') +
  sc +
  north(huambo_shp) +
  scalebar(huambo_shp, dist = 50, dist_unit = "km",
           transform = TRUE, model = "WGS84")

#huambo_unknown_endemicity_map

huambo_raster_map 
huambo_unknown_endemicity_map 

#rm(huambo_oncho_crop,huambo_oncho_point,huambo_oncho_point_df,huambo_raster_map,huambo_unknown_endemicity_map,huambo_unknown_endemicity_map)
```

Both maps show environmental suitability results for Huambo but the map on the left shows the value for each 5x5 km while the map on the right shows the mean value for each of the 6 IUs in Huambo with unknown endemicity and at least one pixel with an environmental suitability score greater than or equal to 71.

The area, and in some cases the population, within each IU is large. We can also look at the environmental suitability for smaller areas to assist with planning.

For this example, we will look at the IU called Bailundo.

```{r cachiungo-only}
cachiungo_oncho_map <- oncho_angola %>% 
  #filter(grepl('Unknown', Endemicity)) %>% 
  #filter(ADMIN1=='Huambo') %>% 
  ggplot() +
  geom_sf(aes(fill=oncho_mean_aw), lwd=1) +
  gghighlight(IUs_NAME=='Bailundo') +
  geom_sf_label_repel(aes(label = IUs_NAME),
                      force = 100, nudge_x = -2, seed = 10) +
  labs(fill='Environmental suitability') +
  theme(legend.position='top') +
  sc +
  north(oncho_angola) +
  scalebar(oncho_angola, dist = 250, dist_unit = "km",
           transform = TRUE, model = "WGS84")

cachiungo_oncho_map
```

By focusing on this IU, we can show the borders associated with the lower level of geography and the 5x5-km results for environmental suitability.

```{r cachiungo-adm3-suitability}

cachiungo_adm3_shp <- read_sf(here('data', 'input', 'shp', 'ago_admbnda_adm3_gadm_ine_ocha_20180904.shp')) %>% 
  filter(ADM2_EN=='Bailundo')

cachiungo_adm3_oncho_crop <- mask(africa_oncho_raster, cachiungo_adm3_shp)
cachiungo_adm3_oncho_crop <- raster::crop(cachiungo_adm3_oncho_crop, cachiungo_adm3_shp)

cachiungo_oncho_point  <-  rasterToPoints(cachiungo_adm3_oncho_crop)
cachiungo_oncho_point_df <-  data.frame(cachiungo_oncho_point)
colnames(cachiungo_oncho_point_df) = c("lon", "lat", "suitability")

cachiungo_map_label <- ggplot() +
  geom_raster(data = cachiungo_oncho_point_df, aes(lon, lat, fill = suitability), alpha = .7) +
  geom_sf_label(data = cachiungo_adm3_shp,aes(label = ADM3_EN)) +
  #scale_fill_fermenter(n.breaks = 5, palette = "YlOrRd", direction = +1) +
  sc + 
  geom_sf(data = cachiungo_adm3_shp, fill = NA) +
  theme_minimal() +
  labs(fill='Environmental suitability') +
  theme(legend.position='top') +
  #blank() +
  north(cachiungo_adm3_shp) +
  scalebar(cachiungo_adm3_shp, dist = 25, dist_unit = "km",
           transform = TRUE, model = "WGS84")

cachiungo_map_label
rm(cachiungo_map_label,cachiungo_adm3_shp,cachiungo_oncho_point,cachiungo_adm3_oncho_crop,cachiungo_oncho_point_df)

```

From this map, we might decide to focus on Bailundo & Lunge as these areas appear to have the highest environmental suitability score.

The Excel file supplied with this document includes the list of 116 IUs with unknown endemicity, the weighted mean environmental suitability score, and the number of locations in each IU exceeding the environmental threshold value of 71.

```{r}

loaloa_summary_df <- ang_espen_loaloa_data %>% select(IU_ID, loaloa_Endemicity=Endemicity)

final_table <- exceeds71_oncho %>% 
  as.data.frame() %>% 
  filter(grepl('Unknown', Endemicity)) %>% 
  left_join(oncho_angola_mean_env_iu, by=c('ADMIN1ID', 'ADMIN2ID', 'ADMIN3ID', 'IU_ID')) %>% 
  left_join(loaloa_summary_df, by=c('IU_ID')) %>% 
  select(ADMIN1,IUs_NAME, PopTot, Endemicity, Enironment_suitability=oncho_mean_aw, locations_exceeding_threshold=n, loaloa_Endemicity)

write.csv(final_table, here('data', 'output', 'ang_oncho_final_table.csv'))

rm(exceeds71_oncho,oncho_angola_mean_env_iu)
```
